Circumnuclear Media and Accretion Rates of Quiescent Supermassive Black Holes

### 2015-04-27 ms.tex
cutting fat - and lots of it8

Shown also for comparison in Figure \ref{fig:bh_growth} (top panel) is
the accretion rate onto SgrA* calculated by \citet{Quataert:2004a}.
Also show is the range of $\dot{M}$ for the low-luminosity AGN NGC3115
derived through detailed modeling by \citet{ShcherbakovWong+:2014a},
who find a range of accretion rates depending on the assumed model for
thermal conductivity\footnote{We expect this range would be have been smaller
had \citet{ShcherbakovWong+:2014a} included saturation of the conductive flux}.  The SgrA* rate
exceeds our estimate of $\dot{M}$ due to the average SFH for the same $M_{\bullet}$ by almost two orders of magnitude.
This discrepancy can in part be understood by the fact that star formation in
the central parsec of the Milky Way cannot be described as
steady-state: feedback is instead dominated by the stellar winds from
the ring of young massive stars of mass $\sim 10^{4}M_{\odot}$ and
estimated age $\sim 10$ Myr (e.g., \citealt{Schodel+07}).  Such a star
formation history is better described by our impulsive (starburst) scenario,
for which the value of $\eta \sim 100$ at $\tau_{\star} = 10^{7}$ yr
(Fig.~\ref{fig:vwImp}) is a factor of $\sim 100$ times higher than the
value of $\eta \sim 1$ predicted in the average SFH case
(Fig.~\ref{fig:vwSources}, bottom panel).

@@

We acknowledge helpful conversations with Greg Bryan, Jules Halpern,
Kathryn Johnston, Jerry Ostriker, and Eliot Quataert.  This work
relied on Columbia University's Yeti computer cluster, and we
acknowledge the Columbia HPC support staff for assistance.  BDM
gratefully acknowledges support from NASA {\it Fermi} grant
NNX14AQ68G, NSF grant AST-1410950, and the Alfred P. Sloan Foundation.

>>>>

Shown also for comparison in Figure \ref{fig:bh_growth} (top panel) is
the accretion rate onto SgrA* calculated by \citet{Quataert:2004a}.
Also show is the range of $\dot{M}$ for the low-luminosity AGN NGC3115
derived through detailed modeling by \citet{ShcherbakovWong+:2014a},
who find a range of accretion rates depending on the assumed model for
thermal conductivity\footnote{We expect this range would be have been smaller
had \citet{ShcherbakovWong+:2014a} included saturation of the conductive flux.}.  The SgrA* rate
exceeds our estimate of $\dot{M}$ due to the average SFH for the same $M_{\bullet}$ by almost two orders of magnitude.
This discrepancy can in part be understood by the fact that star formation in
the central parsec of the Milky Way cannot be described as
steady-state: feedback is instead dominated by the stellar winds from
the ring of young massive stars of mass $\sim 10^{4}M_{\odot}$ and
estimated age $\sim 10$ Myr (e.g., \citealt{Schodel+07}).  Such a star
formation history is better described by our impulsive (starburst) scenario,
for which the value of $\eta \sim 100$ at $\tau_{\star} = 10^{7}$ yr
(Fig.~\ref{fig:vwImp}) is a factor of $\sim 100$ times higher than the
value of $\eta \sim 1$ predicted in the average SFH case
(Fig.~\ref{fig:vwSources}, bottom panel).

@@

We acknowledge helpful conversations with Greg Bryan, Jenny Greene, Jules Halpern,
Kathryn Johnston, Jerry Ostriker, and Eliot Quataert.  This work
relied on Columbia University's Yeti computer cluster, and we
acknowledge the Columbia HPC support staff for assistance.  BDM
gratefully acknowledges support from NASA {\it Fermi} grant
NNX14AQ68G, NSF grant AST-1410950, and the Alfred P. Sloan Foundation.
